Refinements for open pNets

### 2021-07-27 2021-Refinement/paper/refinementarticle.tex
reunion

\subsection{Deadlock Preservation, Reachability, and Composition}

@@

Before characterising a composition which does not introduce deadlocks we need to be able to tell which states are reachable.
\begin{definition}[Reachability]
For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is preserved across transitions, and valdi on initial state:
\[\sigma_0 \vdash \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \vdash \left(\reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\right)\]
\end{definition}
Reachability takes into account all paths, and potentially over-approximate the reachable configurations and must be representable as a formula.
% LUDO HERE
\begin{definition}[Non-locking composition]
Let \(A_i = \OAg[i], 0 \leq i \leq n\).
The composition \(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) 
 is a non-locking composition if if \(A \) has a reachability predicate satisfying the following.
From reachable configurations, if there was a possible transition in \(A_0\) then there is a possible transition in \(A\):
\[ \forall s = \mpar{s_0, s'} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)\]
\end{definition}
Again we use guards as a characteristics that the transition occurs.

@@

>>>>

\subsection{Deadlock Reduction, Reachability, and Composition}

@@

Before characterising a composition which does not introduce deadlocks we need to be able to tell which states are reachable.
\begin{definition}[Reachability]
For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is preserved across transitions, and valid on initial state:
\[\sigma_0 \vdash \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \vdash \left(\reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\right)\]
\end{definition}
Reachability takes into account all paths, and potentially over-approximate the reachable configurations and must be representable as a formula.
% LUDO HERE
\begin{definition}[Non-locking composition]
Let \(A_i = \OAg[i], 0 \leq i \leq n\).
The composition \(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) 
 is a non-locking composition if if \(A \) has a reachability predicate satisfying the following.
From reachable configurations, if there was a possible transition in \(A_0\) then there is a possible transition in \(A\):
\[ \forall s = \mpar{s_0, s'} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)\]
\end{definition}
Again we use guards as a characteristics that the transition occurs.

@@

\TODO{pour rabea}
